Statistical analysis of periodic data in neuroscience

### 2021-06-26 manuscript/manuscript.Rmd
Fixed a typo

To confirm that distributions of F-statistics generated by the $ANOVA^2_{circ}$ test have the expected form, simulations were conducted for a range of study designs. A null bivariate data set was generated for _N_ participants and _k_ groups, using normally distributed random numbers with underlying condition means of 0 for both the real and imaginary components. The F-statistic was then calculated using equations \@ref(eq:Fratio), \@ref(eq:MSM) and \@ref(eq:MSR). This procedure was repeated one million times for twenty combinations of _N_ and _k_, and the distributions summarised using histograms. Figure \@ref(fig:fdistributions) shows the results of these simulations (blue shading), for comparison with analytically derived F-distributions of $df_M = 2(k-1)$ and $df_R = 2((Nk)-k)$ degrees of freedom (black lines, generated using the _df_ function in _R_). The correspondence between the stochastic and analytic distributions is excellent, comfirming that the test produces the expected null distribution of test statistics.

>>>>

To confirm that distributions of F-statistics generated by the $ANOVA^2_{circ}$ test have the expected form, simulations were conducted for a range of study designs. A null bivariate data set was generated for _N_ participants and _k_ groups, using normally distributed random numbers with underlying condition means of 0 for both the real and imaginary components. The F-statistic was then calculated using equations \@ref(eq:Fratio), \@ref(eq:MSM) and \@ref(eq:MSR). This procedure was repeated one million times for twenty combinations of _N_ and _k_, and the distributions summarised using histograms. Figure \@ref(fig:fdistributions) shows the results of these simulations (blue shading), for comparison with analytically derived F-distributions of $df_M = 2(k-1)$ and $df_R = 2((Nk)-k)$ degrees of freedom (black lines, generated using the _df_ function in _R_). The correspondence between the stochastic and analytic distributions is excellent, confirming that the test produces the expected null distribution of test statistics.

### 2021-06-26 manuscript/manuscript.tex
Fixed a typo

To confirm that distributions of F-statistics generated by the \(ANOVA^2_{circ}\) test have the expected form, simulations were conducted for a range of study designs. A null bivariate data set was generated for \emph{N} participants and \emph{k} groups, using normally distributed random numbers with underlying condition means of 0 for both the real and imaginary components. The F-statistic was then calculated using equations \eqref{eq:Fratio}, \eqref{eq:MSM} and \eqref{eq:MSR}. This procedure was repeated one million times for twenty combinations of \emph{N} and \emph{k}, and the distributions summarised using histograms. Figure \ref{fig:fdistributions} shows the results of these simulations (blue shading), for comparison with analytically derived F-distributions of \(df_M = 2(k-1)\) and \(df_R = 2((Nk)-k)\) degrees of freedom (black lines, generated using the \emph{df} function in \emph{R}). The correspondence between the stochastic and analytic distributions is excellent, comfirming that the test produces the expected null distribution of test statistics.

>>>>

To confirm that distributions of F-statistics generated by the \(ANOVA^2_{circ}\) test have the expected form, simulations were conducted for a range of study designs. A null bivariate data set was generated for \emph{N} participants and \emph{k} groups, using normally distributed random numbers with underlying condition means of 0 for both the real and imaginary components. The F-statistic was then calculated using equations \eqref{eq:Fratio}, \eqref{eq:MSM} and \eqref{eq:MSR}. This procedure was repeated one million times for twenty combinations of \emph{N} and \emph{k}, and the distributions summarised using histograms. Figure \ref{fig:fdistributions} shows the results of these simulations (blue shading), for comparison with analytically derived F-distributions of \(df_M = 2(k-1)\) and \(df_R = 2((Nk)-k)\) degrees of freedom (black lines, generated using the \emph{df} function in \emph{R}). The correspondence between the stochastic and analytic distributions is excellent, confirming that the test produces the expected null distribution of test statistics.
